---
title: "p8105_hw1_ren2121"
output: html_document
date: "2025-09-13"
---

# Problem 1

Loading the "moderndive" library and the "early_january_weather" dataset:

```{r}
library(moderndive)
data("early_january_weather")
```

**Description of the "Early January Weather" dataset:**

The variables in the dataset are as follows: `r names(early_january_weather)`.

This dataset has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.

The mean temperature in early January was `r mean(early_january_weather$temp)` degrees.

**Creating a scatterplot**

```{r}
#Loading the library
library(ggplot2)
#Creating the plot
(temp_vs_time <- ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
    geom_point())
#Saving the plot
ggsave("temp_vs_time.pdf", plot = temp_vs_time, height = 4, width = 6)
```

As time (hours) increases, temperature generally increases, but it oscillates up and down along the way. This likely reflects daily rises and falls with the sun.

# Problem 2

Creating a dataframe:

```{r}
library(tidyverse)
my_df = tibble(
  x = rnorm(10),
  x_pos = x > 0,
  vec_char = c("r", "is", "kinda", "hard", "and", "i", "am", "learning", "it", "slowly"),
  vec_factor = factor(c("tea", "coffee", "oj", "oj", "coffee", "tea", "oj", "tea", "coffee", "oj"))
)
```

**Taking the mean of each of my variables:**

Mean of variable x = `r mean(pull(my_df, x))`

Mean of variable x_pos = `r mean(pull(my_df, x_pos))`
  When I take the mean of variable x_pos, a value is returned, however it does not make sense given
  that my variable is a logical vector with values of _true_ and _false_.

When I try to take the mean of vec_char, I get 'NA' using the code 'mean(pull(my_df, vec_char))':
  I cannot take the mean of a character vector, and R tells me that the 'argument is not numeric or
  logical: returning NA.'

Finally, when I try taking the mean of vec_factor, I get an error message using the code 'mean(pull)(my_df, vec_factor)'.
  R tells me that I am attempting to 'apply non-function.'

**Converting variable types:**

```{r results = 'hide', warning = FALSE}
as.numeric(my_df$x_pos)
as.numeric(my_df$vec_char)
as.numeric(my_df$vec_factor)
```

When I try to force convert my variables to numeric type, my factor vector now takes values of 1, 2, or 3.  
>   This makes sense because I created 3 categories, and R simply assigned each category a number.

My x-pos vector now takes values of 0 or 1.  
>   This is because either it is true that a value in my random sample is greater than 0, or it is false. Therefore, R was able to assign 0 or 1 to indicate true or false.

However, when I tried to convert vec_char, each value became an 'NA' and a warning message appeared that  
> read "NAs introduced by coercion".  
>   R could not convert my characters to numbers.

This explains what happens when I try to take the mean of each of my variables, because whether or not R was  
able to complete this task for me depended on whether R could find a way to convert my variables to a  
numeric type.








