---
title: "p8105_hw1_ren2121"
output: html_document
date: "2025-09-13"
---

# Problem 1

Loading the "moderndive" library and the "early_january_weather" dataset:

```{r}
library(moderndive)
data("early_january_weather")
```

**Description of the "Early January Weather" dataset:**

The variables in the dataset are as follows: `r names(early_january_weather)`.

This dataset has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.

The mean temperature in early January was `r mean(early_january_weather$temp)` degrees.

**Creating a scatterplot**

```{r}
#Loading the library
library(ggplot2)
#Creating the plot
(temp_vs_time <- ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
    geom_point())
#Saving the plot
ggsave("temp_vs_time.pdf", plot = temp_vs_time, height = 4, width = 6)
```

As time (hours) increases, temperature generally increases, but it oscillates up and down along the way. This likely reflects daily rises and falls with the sun.

# Problem 2